---
title: "lab-07-simpsons.Rmd"
author: "Ahmed adnan"
date: "17 March 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r load_libraries, message=FALSE}
library(tidyverse) 
library(mosaicData)
```


## Exercises


1.  
```{r whickam}
glimpse(Whickham)
```
    
Your answer: The data is experimental because specific information about the people was collected.

2.  
```{r observations}
nrow(Whickham)
```

Your answer;There are 1,134 rows/observation in this dataset.

3.  

```{r number_variables}
ncol(Whickham)
```

Your answer:there are 3 variables/columns in this dataset.  

```{r var_type}
unique(Whickham$outcome)
unique(Whickham$smoker)
unique(Whickham$age)
```

Your answer: Using the 'unique()' function on the 3 variables, we could see that "outcome" varible only takes Alive or Dead value,which makes it categorical non-ordinal. "smoker" variable only takes Yes or No, which also makes it categorical non-ordinal. Age is numerical continuous data.


One of the best ways to visualize categorical data is through the use of bar charts.



```{r plot_outcome}
ggplot(Whickham, aes(x= outcome)) +
  geom_bar()
```


```{r plot_smoker}
ggplot(Whickham, aes(x= smoker)) +
  geom_bar()
```

```{r plot_age}
ggplot(Whickham, aes(x= age, fill = smoker)) +
  geom_histogram(binwidth =3, color = "black") +
  facet_wrap(~ outcome, nrow = 2)
```


4. 
I expect that there will be more deaths of smoker than there will be of non-smokers.

Knit, commit, and push to github.

5. 

```{r plot_smokeVSincome_2}
Whickham %>%
  count(smoker, outcome)
```

6.

```{r age_cat}

```

7. 

```{r plot_smokeVSincome_3}

```

Knit, commit, and push to github.